Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-10-27 cvpr2018.tex

\section{Preliminary}
\subsection{Generative Adversary Network}
Generative adversary networks (GANs) are composed of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game. The discriminator $D$ is optimized to distinguish the synthesized images from the real images, meanwhile, the generator $G$ is trained to fool the discriminator by trying to convert an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$,
\begin{equation}
\label{game}
\begin{split}
\underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
&\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
\end{split}
\end{equation}
where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.

@@

\section{Method}
Figure \ref{fig:archs} illustrate the overall method.
%To generate high-resolution photo-realistic images from text embeddings, we propose a simple and effective Hierarchically-nested Generative Adversarial Network.
Our approach is to train both generator and discriminator conditioned on sentence embedding vectors. We leverage functional loss for discriminator and hierarchically nested side outputs as hierarchical supervision for both generator and discriminator to achieve our goal of generating photo-realistic images from text descriptions.  In general, the generator takes text embedding and random noise vector as input and synthesis images at different scales (e.g, $64\times64$, $128\times128$, $256\times256$). The discriminator, on the other hand, is trying to judge the pair of synthesized images and the corresponding text embedding as fake pairs as well as differentiating the real images from the fake images. $G$ and $D$ are optimized alternatively until converges.

\textbf{Notation } In this paper, we use the following notations. Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively. Please note that, $G$ has multiple branches and generates multiple images of different sizes and for each image size, we have a distinct $D$. For simplicity, we only describe one image size.

@@

\textbf{Variational text embedding } Following the work of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $\Psi_t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$. This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi_t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}. In addition, using this kind of text embedding makes the input pure stochastic, making it more difficult for the generator to over fit the training data.

\subsection{Scalable Deeply Supervised}
Instead of only predicting the high resolution in the final output, our model is designed to predict multi-level images of gradually increasing dimension (e.g., 256$\times$256 as the final output with 64$\times$64 and 128$\times$128 being the side output).

In principle, the lower-resolution side output is forced to learn the rough structure (e.g., object sketch, color information and background) of the images, the subsequent higher-resolution path is used to add more details to the images.

The lower-level side output works by regularizing the lower-level image feature. Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than stackGan\cite{han2017stackgan}. This type of side output is also proven useful because it allows short path between image supervision information to the hidden feature maps, which could potentially helps training.

\subsection{Generator Loss}
As is shown in Fig\ref{game}, In the generator $G$, we first sample a random vector $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$, then text embedding vector $\psi_{t}$ is obtained by applying an per-trained text encoder on the image description $t$, in this paper, we use the char-rnn based text encoder provided in \cite{reed2016generative}.

Conditioned on variational text embedding $c$ and the random vector $z$, a synthetic image $\hat{x}$ is generated as $\hat{x}\leftarrow G(c,z)$, it is simply a feed forward pass of the generator. The generator $G$ consists of stacks of residual blocks, bilinear sampling layer is used to up-sample the feature maps.

The generator's goal is to generator image that match the input text embedding and looks as real as possible. So the loss function for our model mainly consists of two parts, namely, matching aware loss and one image loss.

Given a set of chosen input pair $(x, \psi_t)$, the generator is optimizing the following function
 \begin{equation}
 \label{genloss}
 \begin{split}
 \mathcal{L}_G = & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{sent}( G(z, c_t),  \psi_t) ) ] + \\
				  & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{img}( G(z, c_t) ) ) ] + \\
                  & D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) 		   
 \end{split}
 \end{equation}
 where $c_t$ is the variational conditional vector generated from $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$. To make the network differentiable, in practice, we adopted the re-parametric trick\cite{vae}, where $c_t$ is actually computed as $\mu(\psi_t)+\Sigma(\psi_t)\odot \epsilon$, where $\epsilon\in \mathcal{R}^{T}$ is draw from a normal Gaussian distribution.

@@

\subsection{Functional Loss of Discriminator}

As is shown in Figure. \ref{overview}, the discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.

Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D$, we first transfer $x$  to an image code $Code_x$. $Code_x$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix. Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake. We performance batch normalization on all convolutional layers. \textcolor{red}{like stackgan, I will add much more architecture details later}

The generator $G$ and discriminator $D$ are optimized alternatively using their corresponding loss function.

 Our goal is to generate images that not only look as realistic as real images, but also matching the given text description.
 Therefore, the discriminator must handle errors of the following two categories: real image with mismatch conditional text information, fake image with real text. In order to achieve this, the previously proposed matching aware discriminator is explicitly trained with three pair configurations, namely: real image with right text as positive training sample, and the aforementioned two sources of error pairs as negative training samples.

 Given a mini-batch of training data consists of images $x$ and the corresponding text $t$, mismatching text $\hat{t}$. First of all, we sample fakes images using $G$.
 $\hat{x_1} = G(z_1, \psi_t)$ and $\hat{x_2} = G(z_2, \psi_t)$, where $z_1$ and $z_2$ are random vector sampled from norm Gaussian distribution.

The loss function of the matching aware discriminator are summarized as:
  \begin{equation}
  \label{matchignloss}
  \begin{split}
  \mathcal{L}_D = 	  &\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
					  &\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D(x, \psi_{\hat{t}} )  ] +\\
					  &   \mathbb{E}_{t \sim p_{data}}[\log(D(\hat{x_1}, \psi_t) ) ] 
  \end{split}
  \end{equation}
This loss explicit force the discriminator to differentiate correct pair from the wrong pair.  However, there is no explicit loss that push the discriminator to differentiate real images from the fake images. The way that they formulate all the task into pair based solution complicate the task of the generator. In this paper, we propose to directly add another loss that concentrate the image quality only beside the matching loss. Specifically, it can be given by:
  \begin{equation}
  \label{discoss}
  \begin{split}
  \mathcal{L}_D = 	&\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
		  &\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D_{pair}(x, \psi_{\hat{t}} )  ] +\\
		  &\mathbb{E}_{t \sim p_{data}}[\log(D_{pair}(\hat{x_1}, \psi_t) ) ] + \\
		  &\mathbb{E}_{x \sim p_{data}}[\log( D_{img}(x) )] - 0.5* ( \\
		  &\mathbb{E}[\log( D_{img}(\hat{x_1}))] + \mathbb{E}[\log( D_{img}(\hat{x_2}) )  ] )
  \end{split}
  \end{equation}
\textcolor{red}{equations needs to be verified, just a rough place holder}

Further more, this separation of the image loss from the matching loss open further possibilities, such as utilizing the unlabeled image to improve both the genrator and discriminator. \textcolor{red}{maybe utilizing the imagenet for training the coco, or save as another paper.}

@@

\subsection{Dataset}
\textbf{Dataset} We use three datasets for evaluation. \textcolor{red}{Yuanpu address}

\subsection{Evaluation metric}
\textbf{Inception score }

@@

\subsection{Case study}
\textbf{Generalization to real user test}
We test the generalization of our method by asking a user to write a sentence

>>>>

\section{Preliminary}
\subsection{Generative Adversary Network}
Generative adversary networks (GANs) are composed of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game. The discriminator $D$ is optimized to distinguish the synthesized images from the real images, meanwhile, the generator $G$ is trained to fool the discriminator by trying to convert an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$,
\begin{equation}
\label{game}
\begin{split}
\underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
&\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
\end{split}
\end{equation}
where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.
In this paper, we replace the negative log likelihood loss with a least square objective\cite{lsgan}.

@@

\section{Method}
Figure \ref{fig:archs} illustrate the overall method.
%To generate high-resolution photo-realistic images from text embeddings, we propose a simple and effective Hierarchically-nested Generative Adversarial Network.
Our approach is to train both generator and discriminator conditioned on sentence embedding vectors. We leverage functional loss for discriminator and hierarchically nested side outputs as hierarchical supervision for both generator and discriminator to achieve our goal of generating photo-realistic images from text descriptions.

In general, the generator takes text embedding and random noise vector as input and synthesis images at different scales (e.g, $64\times64$, $128\times128$, $256\times256$). The discriminator, on the other hand, is trying to judge the pair of synthesized images and the corresponding text embedding as fake pairs as well as differentiating the real images from the fake images. $G$ and $D$ are optimized alternatively until converges.

\textbf{Notation } 
We denote the training data set by $S=\{(\bm{X}^n, \bm{T}^n),n=1,...,N\}$, where $X^n$ is the $n-$th training image, and $T^n={t^1,...,t^m}$ as $m$ text descriptions corresponds to $X^n$. Our goal is to learn the generator $G$ that is capable of producing high resolution images of high visual quality as well as variability giving an input text description $t$.

Denote the image dimension, text embedding dimension and the dimension of the noise input as $I$, $T$ and $Z$, respectively. Please note that, $G$ has multiple branches and generates multiple images of different sizes and for each image size, we have a distinct $D$. For simplicity, we only describe one image size.

@@

\textbf{Variational text embedding } Following the practice of \cite{han2017stackgan}, instead of using the plan deterministic non-linear transformation of the original $\psi_t$, we obtain the conditional vector $c$ by sampling from a Gaussian distribution $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$, in which the mean $\mu(\psi_t)$ and the diagonal covariance matrix $\Sigma(\psi_t)$ are non-linear transformation of the original text embedding $\psi_t$. This type of conditional augmentation technique can be used to inject randomness to the text embedding vector $\psi_t$ to mitigate the common problem that conventional conditional GAN training paradigm usually learns to totally ignore the randomness, resulting to collapsing results lacking diversity \cite{reed2016generative}. In addition, using this kind of text embedding makes the input pure stochastic, making it more difficult for the generator to over fit the training data.

@@

\subsection{Hierarchical Deep Supervision}
Directly predicting high resolution synthesized images are difficult, not only because of the difficulties in training but also due to the large variation and instability in the hidden layers.

Our architecture of $G$ consists of a single stream network with additional multiple side outputs. This architecture resemble the previous proposed method in edge detection\cite{hed} and classification\cite{deepsup}, which demonstrate that additional supervision to the hidden layer can improve both generalization and optimization.  We hypothesis that adding hidden layer supervision using side outputs can act as a regularizer to the hidden space of $G$, which reduces the over-fitting issue and provide a short path for the error signal.

Given a random Gaussian noise  $z\in \mathcal{R}^{Z} \scriptsize{\sim} \mathcal{N}(0,1)$ and a text description $t$, to obtain the text embedding vector $\psi_{t}\in \mathcal{R}^{T}$, we apply a per-trained text encoder on the image description $t$, in this paper, we use the char-rnn based text encoder provided in \cite{reed2016generative}.  $G$ will generate multiple side outputs,
\begin{equation}
\label{side}
\begin{split}
	o_1,...,o_s = G(\psi_{t}, z)	   
\end{split}
\end{equation}
where $s$ is the total number of side outputs, please note that the dimension of $o_1,..,o_s$ increase gradually (e.g., 64$\times$64, 128$\times$128, and 256$\times$256). Denote $\mathcal{X}^i = \{X^i_1, .. X^i_s\}$ as the pyramid of  resized images constructed from original image $X^i$.

For each $o_i$, a distinct discriminator $D_i$ is assigned to compete with it. Denote $\mathcal{D}=\{D_1, ..., D_o\}$ as the whole set of discriminators.
We aim to solve the following optimization problem:

\begin{equation}
\label{equ:optim}
\begin{split}
  G^*, \mathcal{D}^* = \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{L}(G,\mathcal{D}, \mathcal{X}, \bm{T} , z)
\end{split}
\end{equation}
where $\mathcal{D}^*$ compresses the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} , z)$ is the full objective of this mini-max game.

Please note that in this setting, one generator competes with multiple discriminators. And each discriminators does not share weights with each other, thus giving them the flexibility to focus on learning different discriminative features.

In principle, the lower-resolution side output is forced to learn the rough structure (e.g., object sketch, color information and background) of the images, the subsequent higher-resolution path is used to add more details to the images. 
Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than stackGan\cite{han2017stackgan}. This type of side output is also proven useful because it allows short path between image supervision information to the hidden feature maps, which could potentially helps training.

\subsection{Matching Aware Pair-Loss}
During the setting of conditional generative adversarial learning, simply generating images of high visual quality is not enough, most importantly, we want the generated images well aligned with the conditioning information (text description in our model).

%Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D_i$, we first transfer $x$  to an image code $Code_x$. $Code_x$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix. Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake. We performance batch normalization on all convolutional layers. \textcolor{red}{like stackgan, I will add much more architecture details later}  
%
%The generator $G$ and discriminator $D$ are optimized alternatively using their corresponding loss function.

Therefore, the discriminator should be optimized to differentiate two errors: real image with mismatch conditional text information, fake image with real text. In order to achieve this, the previously proposed matching aware discriminator is explicitly trained with three pair configurations, namely: real image with right text as positive training sample, and the aforementioned two sources of error pairs as negative training samples.

Given a mini-batch of training data consists of images $X$ and the corresponding text $t$, mismatching text $\hat{t}$. For simplicity, we omit the instance index.  To train the discriminator,  we also need to sample fakes images $o_i$ using $G$. For the $i-$th discriminator $D_i$ , we can have:

\begin{equation}
\label{equ:matchignloss}
\begin{split}
\mathcal{L}_{pair}(D_i)  = & \mathbb{E}_{(x, t) \sim p_{data}}[(D_i( {X_i},  \bm{t}) - 1) ^ 2 ] - \frac{1}{2}*\\ 
&   \mathbb{E}_{(X_i, \hat{t}) \sim p_{data}}[(D_i({X_i}, \hat{\bm{t}}) - 1)^2  ] - \frac{1}{2} *\\
&   \mathbb{E}_{t \sim p_{data}}[ (D_i( {o}_i, \bm{t}))^2 ]  
\end{split}
\end{equation}

Similarly, the pair wise objective of generator can be summarized as:
\begin{equation}
\label{equ:pariG}
\begin{split}
\mathcal{L}_{pair}(G)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ (D_i( {o}_i, \bm{t}) - 1) )^2 ] )
\end{split}
\end{equation}

This type of loss is used to push the valid image-text pair away from the invalid pairs.

\subsection{Local Adversarial Image Loss}
%As is shown in Figure. \ref{overview}, the discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.

The pair-loss is designed to differentiated invalid pairs from valid ones. However, at the very beginning of the training, the generated images are far away from true image distribution, the discriminator can very easily to judge a pair as valid without using much pair information. \textcolor{red}{need more explanationn.}

Our insight has two folds:
1. Image loss without using pair sentence information can be beneficial in the sense that it utilize more information as well as it directly push the generated image to the true image distribution. We hypothesis this type of loss can help the model to stabilize and boost the training. 
2. Since our model outputs a pyramid of side outputs with increasing image size. We expect the low resolution output can capture the global structure and color information, while the higher resolution outputs paints more details and focus on rendering the image.

We don't only want the whole image is classified as true image by the discriminator, but also restrict the discriminator to classify all the local patches of high resolution output as true as well.   To this end, we propose a hierarchical image loss, where the output of the image  discriminator is more than one scale value.
\begin{equation}
  d_i = D_i(X_i)
\end{equation}
The size of $d_i$ increases as $X_i$. For instance 1$\times$1 for 64$\times$64 input, 4$\times 4$ for 128$\times$128, etc. This type of design, gradually increase the receptive field of the discriminator.

This loss explicit force the discriminator to differentiate correct pair from the wrong pair.  However, there is no explicit loss that push the discriminator to differentiate real images from the fake images. The way that they formulate all the task into pair based solution complicate the task of the generator. In this paper, we propose to directly add another loss that concentrate the image quality only beside the matching loss. Specifically, it can be given by:
\begin{equation}
\label{equ:local}
\begin{split}
\mathcal{L}_{local}(K_i)  = & \mathbb{E}_{(x, t) \sim p_{data}}[(K_i( {X_i}) - 1) ^ 2 ] -  \mathbb{E}_{t \sim p_{data}}[ (K_i( {o}_i))^2 ]  
\end{split}
\end{equation}

Similarly, the pair wise objective of generator can be summarized as:
\begin{equation}
\label{equ:pariG}
\begin{split}
\mathcal{L}_{local}(G)  = & \sum_{i=1}^{s} ( \mathbb{E}_{t \sim p_{data}}[ (K_i( {o}_i) - 1) )^2 ] )
\end{split}
\end{equation}

\textcolor{red}{equations needs to be verified, just a rough place holder}

Further more, this separation of the image loss from the matching loss open further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator. \textcolor{red}{maybe utilizing the imagenet for training the coco, or save as another paper.}

\subsection{Total Loss}
The total objective for both $D$ and $G$ can be given by. 
\begin{equation}
\label{equ:totalD}
\begin{split}
\mathcal{L}(D)  = & \sum_{i=1}^{s} ( \mathcal{L}_{pair}(D) + \alpha~\mathcal{L}_{local}(D) ) 
\end{split}
\end{equation}

\begin{equation}
\label{equ:totalG}
\begin{split}
\mathcal{L}(G)  = & \sum_{i=1}^{s} ( \mathcal{L}_{pair}(G) + \alpha~\mathcal{L}_{local}(G) + \\
                  & \beta~D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) )  
\end{split}
\end{equation}
where $\alpha$ is coefficient used to tune the weight of the local patch loss, $\beta$ is used to tune the weights of the KL-Divergence.  A algorithm that summarizes the training process of our model is given in Algorithm 1.

%The loss function of the matching aware discriminator are summarized as:
%\begin{equation}
%\label{matchignloss}
%\begin{split}
%\mathcal{L}_D = 	  &\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
%&\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D(x, \psi_{\hat{t}} )  ] +\\
%&   \mathbb{E}_{t \sim p_{data}}[\log(D(\hat{x_1}, \psi_t) ) ] 
%\end{split}
%\end{equation}
%
%\begin{equation}
%\label{matchignloss}
%\begin{split}
%\mathcal{L}_D = 	  &\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
%&\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D(x, \psi_{\hat{t}} )  ] +\\
%&   \mathbb{E}_{t \sim p_{data}}[\log(D(\hat{x_1}, \psi_t) ) ] 
%\end{split}
%\end{equation}

\subsection{Implementation Details}
\begin{equation}
 \label{genloss}
 \begin{split}
 \mathcal{L}_G = & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{sent}( G(z, c_t),  \psi_t) ) ] + \\
				  & \mathbb{E}_{z\sim p_{z}, t \sim p_{data}}[-\log( D_{img}( G(z, c_t) ) ) ] + \\
                  & D_{KL}(\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )|| \mathcal{N}(0, \bm{I})) 		   
 \end{split}
 \end{equation}
 where $c_t$ is the variational conditional vector generated from $\mathcal{N}(\mu(\psi_t), \Sigma(\psi_t) )$. To make the network differentiable, in practice, we adopted the re-parametric trick\cite{vae}, where $c_t$ is actually computed as $\mu(\psi_t)+\Sigma(\psi_t)\odot \epsilon$, where $\epsilon\in \mathcal{R}^{T}$ is draw from a normal Gaussian distribution.

@@

\subsection{Dataset}
\textbf{Dataset} 
We evaluate our method extensively using three widely used datasets.  CUB dataset contains 11,788 bird images belonging to one of the 200 different classes. Each image in this dataset is associated with 10 text descriptions. We pre-process the image using the same pipeline proposed in \cite{han2017stackgan}, which crops the birds foreground out to  ensure a object-background ratio greater than 0.75.  The OXford-102 dataset contains 102 different categories of flowers with 8189 images in total. Following the similar experiment setting in \cite{han2017stackgan, reed2016generative}, we split both of these datasets into class-disjoint training and testing sets. Each image in both CUB and Oxford-102 is associated with 10 text descriptions. We also exploit the MS  COCO dataset, which contains a much more broad image category and various backgrounds. We use the training and validation splitting setting provided by the original COCO dataset, resulting to a training set containing 80k images and a validation set with 40k images.  Different from CUB and Oxford-102, each image in COCO has 5 text descriptions. 
For text features, we use the pre-trained text encoder model provided in \cite{reed2016generative}, each text description is encoded into a 1024 vector.
During the training stage, we randomly pick-up a crop view from the original images, and pick 4 image sentence embedding and use the mean as conditioning vector.

\subsection{Evaluation metric}
\textbf{Inception score. }  To evaluate the quality of generated images, we resort to the recently proposed qualitative evaluation measurement "inception score"\cite{improvedGAN},
 \begin{equation}
	IS = \exp(\mathbb{E}_xD_{\bm{KL}}(p(y|\bm{x})||p(y)))
 \end{equation}
 where $\bm{x}$ denotes generated sample images, $y$ the class label, $p(y|\bm{x})$ represents the conditional label distribution calculated by the Inception model\cite{inception}. Inception score is found to be a good measurement of both objectiveness and diversity of generated images, it is closely correlated with human judgment on the image quality.  For CUB and oxford-102, we use the inception model provided by \cite{han2017stackgan}, for MS COCO dataset, we use the model train on ImageNet.

\textbf{Image-sentence distance. } Since inception score can not measure alignment between the generated images and the text description, here, we conduct a new qualitative measurement, which calculated the cosine distance between image code and the sentence vector. We train the model on each dataset.

\textbf{zizhao's new evaluation methods.}

\textbf{Image retrieval. } We also conduct image retrieval evaluation on the dataset. The results is shown in Fig1.

We only conduct qualitative experiment on

@@

\subsection{Case study}
\textbf{Generalization to real user test}
We test the generalization of our method by asking a user to write a sentence, and the generated results are shown in .
